Proposal Thesis

### 2023-06-01 Thesis/Proposal Thesis/Present/Proposal Thesis.Rmd
Draft
Update
New
Sampe data
Squedula

# _References_

>>>>

# DATA YANG DIGUNAKAN

# DATA YANG DIGUNAKAN

## Data terkait Spesifikasi Bahan Baku

```{r,include=FALSE}
library(readxl)
library(dplyr)

nama   = "~/209_ITB/Thesis/Penelitian Mandiri V dan VII/data input.xlsx"
sheets = excel_sheets(nama)

# ambilin data
df_1 = read_excel(nama,sheet = sheets[1]) # ambil spek
df_2 = read_excel(nama,sheet = sheets[2]) # ambil matriks gula x produk
df_3 = read_excel(nama,sheet = sheets[3]) # ambil matriks produk x minggu

df_1 = df_1 %>% rename(bahan_baku = code_gula,
                       harga      = harga_gula) %>% 
       select(-multiplicator,-cost_obj_func)

colnames(df_2)[2:7] = paste0("bahan_baku_",1:6)

```

# _REFERENCES_
